### 2011-05-12 paper.tex
proofread a bunch, also rearranged some stuff in the oracle section

\begin{lemma}\label{collapse}
Let $C$ be a complexity class closed under polynomial time reductions. Then $\Sigma\cdot\Sigma\cdot C = \Sigma\cdot C$, $\Pi\cdot\Pi\cdot C = \Pi\cdot C$, $\parity\cdot\parity\cdot C = \parity\cdot C$, and $\strongbp\cdot\strongbp\cdot C = \strongbp \cdot C$.
\end{lemma}
\begin{proof}
We begin with $\Sigma\cdot\Sigma\cdot C = \Sigma\cdot C$. Clearly, we have $\Sigma\cdot C \subseteq \Sigma\cdot\Sigma\cdot C$ as we can ignore the added input $y$. Now let $f$ be a partial function in $\Sigma\cdot\Sigma\cdot C$. Then we have a function $g \in \Sigma \cdot C$ such that if $f(x) = 1$ then there exists $y$ of length $p(|x|)$ such that $g(\langle x,y\rangle) = 1$ and if $f(x) = 1$, then for all such $y$ we have $g(\langle x,y\rangle) = 0$. This in turn means that there is a function $h \in C$ such that if $f(x) = 1$ then there exists $y$ of length $p(|x|)$ and $z$ of length $p'(|x|)$ such that $h(\langle x, y, z\rangle) = 1$ and if $f(x) = 0$ then for all such $y,z$ we have $h(\langle x,y,z\rangle) = 0$. Because $C$ is closed under polynomial time reductions, we can instead write this as the function $h'(\langle x,yz\rangle)$, where $yz$ is the concatenation of $y$ and $z$, and thus has length $p(|x|) + p'(|x|)$, and $h' \in C$.Then if $f(x) = 1$, there exists a string $w$ of length $p(|x|)+p'(|x|)$ such that $h'(\langle x,w\rangle) = 1$ and if $f(x) = 0$, for all such strings $w$ we have $h'(\langle x,w\rangle) = 0$, so $f \in \Sigma \cdot C$.

The proof for $\Pi\cdot\Pi\cdot C = \Pi\cdot C$ is similar, and the proof for $\parity\cdot\parity\cdot C = \parity\cdot C$ goes the same way but noting at the end that the sum of an odd number of odd quantities is odd. The proof of $\strongbp\cdot\strongbp\cdot C = \strongbp\cdot C$ again goes the same way, but this time we make $g$ and $h$ wrong with less than half of the desired error rate, and then do a union bound at the end to ensure that we are correct sufficiently often.
\end{proof}

@@

\begin{lemma}\label{interchange}
Let $C$ be a complexity class closed under polynomial time reductions. Then $\Sigma\cdot\strongbp\cdot C \subseteq \strongbp\cdot\Sigma\cdot C$, $\Pi\cdot\strongbp\cdot C \subseteq \strongbp\cdot\Pi\cdot C$, and $\parity\cdot\strongbp\cdot C \subseteq \strongbp\cdot\parity\cdot C$.
\end{lemma}
\begin{proof}
Let us work through the proof for $\Sigma\cdot\strongbp\cdot C$. Let $f \in \Sigma\cdot\strongbp\cdot C$ and let $q$ be a polynomial. Then there exists a polynomial $p$ and $g \in \strongbp\cdot C$ such that if $f(x) = 1$ then there exists $y$ with length $p(|x|)$ such that $g(\langle x, y\rangle) = 1$ and if $f(x) = 0$ then for every $y$ of length $p(|x|)$, we have $g(\langle x, y\rangle) = 0$. Now since $g \in \strongbp\cdot C$, we have a function $h \in C$ and a polynomial $r(|x|)$ such that $h(\langle x,y,z\rangle) = g(\langle x,y\rangle)$ with probability at least $1 - 2^{-(p(|x|)+q(|x|))}$. In particular, if $f(x) = 1$, then there exists a $y$ such that $h(\langle x,y,z\rangle) = 1$ for at least $1-2^{-(p(|x|)+q(|x|))}$ of the $z$, and if $f(x) = 0$, then the total portion of the $(y,z)$ pairs that can have $h(\langle x,y,z\rangle) = 1$ is at most $2^{p(|x|)}\cdot2^{-(p(|x|)+q(|x|))} = 2^{-q(|x|)}$. Therefore, if we choose a $z$ at random, the probability that there is a $y$ with $h(\langle x, y, z\rangle) = 1$ is at most $2^{-q(|x|)}$. We then consider the function $g'(\langle x,z\rangle)$ which is $1$ if there exists a $y$ such that $h(\langle x,y,z\rangle) = 1$ and $0$ otherwise. Clearly $g' \in \Sigma \cdot C$. By the above argument, $g'(\langle x,z\rangle)$ agrees with $f(x)$ with probability at least $2^{-q(|x|)}$. Since this construction works for any $q$, we have $f \in \strongbp \cdot \Sigma \cdot C$.

The other results follow similarly.
\end{proof}

@@

To show that a class is amplifiable, we need the concept of a majority reduction.
\begin{definition}\label{defmajority}
We say that a complexity class $C$ is \emph{closed under majority reductions} if for any partial function $f \in C$, the partial function $\majority(f)$ defined by
$$\majority(f)(\langle x_1, \ldots, x_k\rangle) = 
\begin{cases}1 & \text{ if the number of $i$ such that }f(x_i) = 1\text{ is at least $\frac{k}{2}$} \\
0 & \text{ if the number of $i$ such that }f(x_i) = 0\text{ is more than $\frac{k}{2}$}\\
\x & \text{ otherwise}
\end{cases}$$
is in $C$.
\end{definition}
Now, we see that majority reductions are exactly what we want for amplification:
\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions and polynomial time reductions, then \emph{$f\in\strongbp \cdot C$.}
\end{lemma}
\begin{proof}
This is now the same application of the Chernoff bound which shows that $\bp \cdot \p = \strongbp \cdot \p$. Suppose $f$ is a partial function in $\bp \cdot C$. Then there is a partial function $g$ in $C$ such that $\pr_y [g(\langle x,y\rangle) = 1] > 2/3$ if $f(x) = 1$ and $\pr_y [g(\langle x, y\rangle) = 0] > 2/3$ if $f(x) = 0$, where the length of $y$ is equal to $p(|x|)$ for some polynomial $p$. Let $q$ be a polynomial, where $e^{-q(|x|)}$ is the desired error probability. Let $k = 48q(|x|)$.

Here is how we determine the value $f(x)$ with error probability $e^{-q(|x|)}$. Choose $k$ strings $y_1,y_2,...,y_k$ randomly, then return $h(\langle x, y_1y_2\cdots y_k\rangle) = \majority(g)(\langle \langle x, y_1 \rangle, \langle x, y_2 \rangle, \ldots, \langle x, y_k \rangle \rangle)$. Notice that $h$ can be easily reduced to $\majority(g)$ in polynomial time, and is therefore in $C$.
Let $X_i$ be an indicator variable which is $1$ if $g(\langle x,y_i\rangle)$ agrees with $f(x)$. We have that the $X_i$ are independent Bernoulli random variables with $\pr\left[X_i = 1\right] > \frac{2}{3}$.  Then by the Chernoff bound,
\begin{align*}
\pr\left[\sum X_i < k/2\right] &= \pr\left[\sum X_i < (1 - 1/4)(2k/3)\right]\\
&< e^{-(1/4)^2 (2k/3) / 2}\\
&= e^{-q(|x|)} \\
&< 2^{-q(|x|)}
\end{align*}
We can do this for any polynomial $q$, so $f \in \strongbp \cdot C$. Thus, $\bp \cdot C = \strongbp \cdot C$.
\end{proof}

@@

By assumption, $C$ is closed under majority reductions and under intersection. Thus,\linebreak $\intersect(\majority(g)) \in C$. We want to show that $\intersect(f) \in \bp\cdot C$. For any $(x_1,x_2,...,x_k)$, we randomly choose random strings $y_{i,j}$ of length $p(|x_i|)$, for $1\le i\le k$ and $j\le 1\le \ell$, where $\ell = \lceil -48\ln(1 - (2/3)^{1/k}) \rceil$. Then, we check $\intersect(\majority(g))(\langle X_1, X_2, ..., X_k\rangle)$, where
\begin{center}
$X_i = \langle\langle x_i,y_{i,1}\rangle,\langle x_{i},y_{i,2}\rangle,...,\langle x_{i},y_{i,\ell}\rangle\rangle$.
\end{center}
By the Chernoff bound, as in the proof of Lemma \ref{majorityimpliesamplify}, we have that $\majority(M)(X_i) = f(x_i)$ with probability greater than $e^{-(1/4)^2 (2\ell/3)/2} \ge 1 - (2/3)^{1/k}$. If $f(x_i) = 1$ for all $i$, then the probability that there exists some $i$ for which $\majority(g)(X_i) \ne 1$ is therefore greater than $((2/3)^{1/k})^k = 2/3$. If there is some $i$ for which $f(x_i) = 0$, then there is a $1 - (2/3)^{1/k} \ge 2/3$ chance that $\majority(g)(X_i) = 0$.

@@

\item[(iv)] Finally, we consider $\parity \cdot C$. If $f \in \parity \cdot C$, then there is a partial function $g \in C$ and a polynomial $p$ such that $f(x) = 1$ if and only if an odd number of $y \in \{0,1\}^{p(|x|)}$ and are such that $g(\langle x, y\rangle) = 1$, and $f(x) = 0$ if and only if there are an even number (but if $g(\langle x,y\rangle) = \x$ for any $y$, then $f(x) = \x$). We want to show that $\intersect(f)$ is in $\parity \cdot C$. Say we have $x_1,x_2,...,x_k$ and we need to verify that all of them are in $f$. Then, accept if there are an odd number of sequences $y_1,y_2,...,y_k$ such that $\intersect(g)(\langle\langle x_1,y_1\rangle,\langle x_2,y_2\rangle,...,\langle x_k,y_k\rangle\rangle) = 1$. To see why this works, let $\# x_i$ be the number of $y_i$ for which $g(\langle x_i,y_i\rangle) = 1$. Then, the number of sequences $y_1,y_2,...,y_k$ for which $\intersect(g)(\langle\langle x_1,y_1\rangle,\langle x_2,y_2\rangle,...,\langle x_k,y_k\rangle\rangle) = 1$ is equal to $(\# x_1)(\# x_2)...(\# x_k)$ which is odd if and only if $\# x_i$ is odd for all $i$.
\end{enumerate}
\end{proof}

@@

%\begin{center}
%$\pr[M\text{ accepts }(x,y)] > 2/3$ if $L$ accepts $x$,\\
%$\pr[M\text{ rejects }(x,y)] > 2/3$ if $L$ rejects $x$.
%\end{center}
For any $\langle x_1,x_2,...,x_k\rangle$, we randomly choose random strings $y_{i,j}$ of length $p(|x_i|)$, for $1\le i\le k$ and $j\le 1\le \ell$, where $\ell = \lceil -48\ln(1 - (2/3)^{1/k}) \rceil$.
Now, $\majority(\majority(g)) \in C$, since $C$ is closed under majority reductions. By the Chernoff bound, (as in Lemma \ref{intersectionlemma}) there is at least a $1-(2/3)^{1/k}$ probability that some $X_i = \langle\langle x_i,y_{i,1}\rangle, \langle x_i, y_{i,2}\rangle,...,\langle x_i, x_{i,\ell}\rangle\rangle$ is ``correct," by which we mean that $\majority(g)(X_i) = f(x_i)$.

@@

\begin{theorem}\label{oracleparityc}
%Let $C$ be a class containing \emph{$\p$} which is closed under intersection. Then\linebreak \emph{$\parity \cdot (\p^{\parity \cdot C}) = \parity \cdot C$}.
%Let $C$ be a $\{\Sigma,\Pi,\parity\}$-constructible class. Then \emph{$ \p^{\parity \cdot C} = \parity \cdot C$}.
Let $C$ be a class containing \emph{$\p$} which is closed under intersection and such that every function in $C$ is defined everywhere (no \emph{$\x$}'s). Then \emph{$ \p^{\parity \cdot C} = \parity \cdot C$}.
\end{theorem}
\begin{proof}
The direction $\parity \cdot C \subseteq \p^{\parity \cdot C}$ is trivial. Let us consider the interesting direction\linebreak $\p^{\parity \cdot C}\subseteq \parity\cdot C$.

Suppose $f \in \parity \cdot (P^{\parity\cdot C})$. Then, there is some polynomial time turing machine $T$, equipped with an oracle to some function $g\in \parity\cdot C$, which accepts $x$ if $f(x) = 1$ and rejects $x$ if $f(x) = 0$.

@@

Also find the strings $x_1,x_2,...,x_{p(|x|)}$ which are the inputs that $T$ would query to the oracles. These may depend on the $a_i$. We now want to verify that the oracle calls are correct. Say that $(a_i, b_i, y_i)$ is \emph{good} if either
\begin{itemize}
\item $b_i = 0$, and both $a_i = 0$ and $y_i = 0^{r(q(|x|))}$, or
\item $b_i = 1$ and $h(x_i, y_i)$
\end{itemize}
Reject if any $(a_i, b_i, y_i)$ is not good. To determine if they are all good, we will have to check some pairs $(x_i, y_i)$ to see if $h(x_i,y_i) = 1$. We can do this with a call to $\intersect(h)$.

@@

We can use this remarkable fact to finish the proof of Lemma \ref{amplifymainlemma}, thus proving Theorem \ref{amplify}.
\begin{proof}[Proof of Lemma \ref{amplifymainlemma} (iv)]
Take any function $f \in \parity \cdot C$. If $C$ is $\{\Sigma, \Pi, \parity\}$-constructible, we can extend $f$ to some $\overline{f}$ which is defined everywhere; i.e. $\overline{f}(x) \ne \x$ for all $x$. To extend $f$ in this way, we simply extend the innermost $\p$ function (see Remark \ref{equivtoold}).

Now, we will show that $\majority(\overline{f})$ is in $\parity \cdot C$. It is easy to see that $\majority(\overline{f}) \in \p^{\parity \cdot C}$. For a given $k$-tuple $(x_1,x_2,...,x_k)$, we use the oracle call to $\parity \cdot C$ to determine how many of the $x_i$ are such that $\overline{f}(x) = 1$ and how many are such that $\overline{f}(x) = 0$. If at least half are accepted, we accept, and if more than half are rejected, we reject.

Thus, $\majority(\overline{f}) \in \p^{\parity \cdot C}$. Thus, we can apply Theorem \ref{oracleparityc} to get that $\majority(\overline{f}) \in \parity \cdot C$. But $\majority(\overline{f})$ is just an extension of $\majority(f)$, so $\majority(f) \in \parity \cdot C$. Therefore $\parity \cdot C$ is closed under majority reductions.
\end{proof}

>>>>

\begin{prop}\label{collapse}
Let $C$ be a complexity class. Then $\Sigma\cdot\Sigma\cdot C = \Sigma\cdot C$, $\Pi\cdot\Pi\cdot C = \Pi\cdot C$, and $\strongbp\cdot\strongbp\cdot C = \strongbp \cdot C$.
\end{prop}

@@

\begin{prop}\label{interchange}
Let $C$ be a complexity class. Then $\Sigma\cdot\strongbp\cdot C \subseteq \strongbp\cdot\Sigma\cdot C$, $\Pi\cdot\strongbp\cdot C \subseteq \strongbp\cdot\Pi\cdot C$, and $\parity\cdot\strongbp\cdot C \subseteq \strongbp\cdot\parity\cdot C$.
\end{prop}

All of these results are not difficult to verify.

@@

To show that a class is amplifiable, we need the concept of a majority reduction.
\begin{definition}\label{defmajority}
We say that a complexity class $C$ is \emph{closed under majority reductions} if for any partial function $f \in C$, the partial function $\majority(f)$ defined by
$$\majority(f)(\langle x_1, \ldots, x_k\rangle) = 
\begin{cases}1 & \text{ if the number of $i$ such that }f(x_i) = 1\text{ is at least $\frac{k}{2}$} \\
0 & \text{ if the number of $i$ such that }f(x_i) = 0\text{ is more than $\frac{k}{2}$}\\
\x & \text{ otherwise}
\end{cases}$$
is in $C$.
\end{definition}
Now, we see that majority reductions are exactly what we want for amplification:
\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions and polynomial time reductions, then \emph{$f\in\strongbp \cdot C$.}
\end{lemma}
\begin{proof}
This is now the same application of the Chernoff bound which shows that $\bp \cdot \p = \strongbp \cdot \p$. Suppose $f$ is a partial function in $\bp \cdot C$. Then there is a partial function $g$ in $C$ such that $\pr_y [g(\langle x,y\rangle) = f(x)] > 2/3$ if $f(x) \ne \x$, where the length of $y$ is equal to $p(|x|)$ for some polynomial $p$. Let $q$ be a polynomial, where $e^{-q(|x|)}$ is the desired error probability. Let $k = 48q(|x|)$.

Here is how we determine the value $f(x)$ with error probability $e^{-q(|x|)}$. Choose $k$ strings $y_1,y_2,...,y_k$ randomly, then return $h(\langle x, y_1y_2\cdots y_k\rangle) = \majority(g)(\langle \langle x, y_1 \rangle, \langle x, y_2 \rangle, \ldots, \langle x, y_k \rangle \rangle)$. Notice that $h$ can be easily reduced to $\majority(g)$ in polynomial time, and is therefore in $C$.
Let $X_i$ be an indicator variable which is $1$ if $g(\langle x,y_i\rangle)$ agrees with $f(x)$. We have that the $X_i$ are independent Bernoulli random variables with $\pr\left[X_i = 1\right] > \frac{2}{3}$.  Then by the Chernoff bound,
\begin{align*}
\pr\left[\sum X_i \le k/2\right] &= \pr\left[\sum X_i \le (1 - 1/4)(2k/3)\right]\\
&< e^{-(1/4)^2 (2k/3) / 2}\\
&= e^{-q(|x|)} \\
&< 2^{-q(|x|)}
\end{align*}
We can do this for any polynomial $q$, so $f \in \strongbp \cdot C$. Thus, $\bp \cdot C = \strongbp \cdot C$.
\end{proof}

@@

By assumption, $C$ is closed under majority reductions and under intersection. Thus,\linebreak $\intersect(\majority(g)) \in C$. We want to show that $\intersect(f) \in \bp\cdot C$. For any $(x_1,x_2,...,x_k)$, we randomly choose random strings $y_{i,j}$ of length $p(|x_i|)$, for $1\le i\le k$ and $j\le 1\le \ell$, where $\ell = \lceil -48\ln(1 - (2/3)^{1/k}) \rceil$. Then, we check $\intersect(\majority(g))(\langle X_1, X_2, ..., X_k\rangle)$, where
\begin{center}
$X_i = \langle\langle x_i,y_{i,1}\rangle,\langle x_{i},y_{i,2}\rangle,...,\langle x_{i},y_{i,\ell}\rangle\rangle$.
\end{center}
By the Chernoff bound, as in the proof of Lemma \ref{majorityimpliesamplify}, we have that $\majority(g)(X_i) = f(x_i)$ with probability greater than $e^{-(1/4)^2 (2\ell/3)/2} \ge 1 - (2/3)^{1/k}$. If $f(x_i) = 1$ for all $i$, then the probability that there exists some $i$ for which $\majority(g)(X_i) \ne 1$ is therefore greater than $((2/3)^{1/k})^k = 2/3$. If there is some $i$ for which $f(x_i) = 0$, then there is a $1 - (2/3)^{1/k} \ge 2/3$ chance that $\majority(g)(X_i) = 0$.

@@

\item[(iv)] Finally, we consider $\parity \cdot C$. If $f \in \parity \cdot C$, then there is a partial function $g \in C$ and a polynomial $p$ such that $f(x) = 1$ if and only if an odd number of $y \in \{0,1\}^{p(|x|)}$ and are such that $g(\langle x, y\rangle) = 1$, and $f(x) = 0$ if and only if there are an even number (but if $g(\langle x,y\rangle) = \x$ for any $y$, then $f(x) = \x$). We want to show that $\intersect(f)$ is in $\parity \cdot C$. Say we have $x_1,x_2,...,x_k$ and we need to verify that all of them are in $f$. Then, accept if there are an odd number of sequences $y_1,y_2,...,y_k$ such that $\intersect(g)(\langle\langle x_1,y_1\rangle,\langle x_2,y_2\rangle,...,\langle x_k,y_k\rangle\rangle) = 1$. To see why this works, let $\# x_i$ be the number of $y_i$ for which $g(\langle x_i,y_i\rangle) = 1$. Then, the number of sequences $y_1,y_2,...,y_k$ for which $\intersect(g)(\langle\langle x_1,y_1\rangle,\langle x_2,y_2\rangle,...,\langle x_k,y_k\rangle\rangle) = 1$ is equal to $(\# x_1)(\# x_2)\cdots(\# x_k)$ which is odd if and only if $\# x_i$ is odd for all $i$.
\end{enumerate}
\end{proof}

@@

%\begin{center}
%$\pr[M\text{ accepts }(x,y)] > 2/3$ if $L$ accepts $x$,\\
%$\pr[M\text{ rejects }(x,y)] > 2/3$ if $L$ rejects $x$.
%\end{center}
For any $\langle x_1,x_2,...,x_k\rangle$, we randomly choose random strings $y_{i,j}$ of length $p(|x_i|)$, for $1\le i\le k$ and $j\le 1\le \ell$, where $\ell = \lceil -48\ln(1 - (2/3)^{1/k}) \rceil$.
Now, $\majority(\majority(g)) \in C$, since $C$ is closed under majority reductions. By the Chernoff bound, (as in Lemma \ref{intersectionlemma}) for any $i$ there is at least a $1-(2/3)^{1/k}$ probability that some $X_i = \langle\langle x_i,y_{i,1}\rangle, \langle x_i, y_{i,2}\rangle,...,\langle x_i, x_{i,\ell}\rangle\rangle$ is ``correct," by which we mean that $\majority(g)(X_i) = f(x_i)$.

@@

\begin{theorem}\label{oracleparityc}
%Let $C$ be a class containing \emph{$\p$} which is closed under intersection. Then\linebreak \emph{$\parity \cdot (\p^{\parity \cdot C}) = \parity \cdot C$}.
%Let $C$ be a $\{\Sigma,\Pi,\parity\}$-constructible class. Then \emph{$ \p^{\parity \cdot C} = \parity \cdot C$}.
Let $C$ be a class which is closed under polynomial reductions and is closed under intersection and such that every function in $C$ can be extended to a function which is defined everywhere (replacing all \emph{$\x$}'s with $0$s and $1$s) which is also in $C$. Then \emph{$ \p^{\parity \cdot C} = \parity \cdot C$}.
\end{theorem}
\begin{proof}
The direction $\parity \cdot C \subseteq \p^{\parity \cdot C}$ is trivial. Let us consider the interesting direction\linebreak $\p^{\parity \cdot C}\subseteq \parity\cdot C$.

Suppose $f \in \parity \cdot (P^{\parity\cdot C})$. We can assume without loss of generality that $f$ is defined everywhere (i.e. $f(x) \ne \x$ for all $x$). If $f$ was not defined somewhere, we could extend it to some $\overline{f}$ which is defined everywhere and agrees with $f$ everywhere that $f$ is defined. Then we could show that $\overline{f} \in \parity \cdot C$, and then we would have $f \in \parity \cdot C$.

Thus, we now assume that $f$ is defined everywhere. Then, there is some polynomial time turing machine $T$, equipped with an oracle to some function $g\in \parity\cdot C$, which accepts $x$ if $f(x) = 1$ and rejects $x$ if $f(x) = 0$.

@@

Also find the strings $x_1,x_2,...,x_{p(|x|)}$ which are the inputs that $T$ would query to the oracles. These may depend on the $a_i$. We now want to verify that the oracle calls are correct. Say that $(a_i, b_i, y_i)$ is \emph{good} if either
\begin{itemize}
\item $b_i = 0$, and both $a_i = 0$ and $y_i = 0^{r(q(|x|))}$, or
\item $b_i = 1$ and $h(x_i, y_i)$.
\end{itemize}
Reject if any $(a_i, b_i, y_i)$ is not good. To determine if they are all good, we will have to check some pairs $(x_i, y_i)$ to see if $h(x_i,y_i) = 1$. We can do this with a call to $\intersect(h)$.

@@

We can use this remarkable fact to finish the proof of Lemma \ref{amplifymainlemma}, thus proving Theorem \ref{amplify}.
\begin{proof}[Proof of Lemma \ref{amplifymainlemma} (iv)]
Since $C$ is $\{\Sigma,\Pi,\parity\}$-constructible, it is the case that any function in $C$ can be extended to be defined everywhere. To see this, we simply take any function in $C$ and extend its innermost $\p$ function (see Remark \ref{equivtoold}), giving us the entire definition. The $\Sigma$, $\Pi$, and $\parity$ operators all have the property that they can precisely define a function given the one on the next level. Therefore, by Theorem \ref{oracleparityc}, we have that $\p^{\parity\cdot C} = \parity\cdot C$.

Now, we will show that $\majority(f)$ is in $\parity \cdot C$. It is easy to see that $\majority(f) \in \p^{\parity \cdot C}$. For a given $k$-tuple $(x_1,x_2,...,x_k)$, we use the oracle call to $\parity \cdot C$ to determine how many of the $x_i$ are such that $f(x) = 1$ and how many are such that $f(x) = 0$. If at least half are accepted, we accept, and if more than half are rejected, we reject.

Thus, $\majority(f) \in  \p^{\parity \cdot C}$, so $\majority(f) \in \parity \cdot C$. Therefore, $\parity \cdot C$ is closed under intersection.
%Take any function $f \in \parity \cdot C$. If $C$ is $\{\Sigma, \Pi, \parity\}$-constructible, we can extend $f$ to some $\overline{f}$ which is defined everywhere; i.e. $\overline{f}(x) \ne \x$ for all $x$. To extend $f$ in this way, we simply extend the innermost $\p$ function (see Remark \ref{equivtoold}).
%
%Now, we will show that $\majority(\overline{f})$ is in $\parity \cdot C$. It is easy to see that $\majority(\overline{f}) \in \p^{\parity \cdot C}$. For a given $k$-tuple $(x_1,x_2,...,x_k)$, we use the oracle call to $\parity \cdot C$ to determine how many of the $x_i$ are such that $\overline{f}(x) = 1$ and how many are such that $\overline{f}(x) = 0$. If at least half are accepted, we accept, and if more than half are rejected, we reject.
%
%Thus, $\majority(\overline{f}) \in \p^{\parity \cdot C}$. Thus, we can apply Theorem \ref{oracleparityc} to get that $\majority(\overline{f}) \in \parity \cdot C$. But $\majority(\overline{f})$ is just an extension of $\majority(f)$, so $\majority(f) \in \parity \cdot C$. Therefore $\parity \cdot C$ is closed under majority reductions.
\end{proof}
